Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-09 paper/sec-analysis.tex
work on paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.65\textwidth]{plots/overlap_categories_C1.pdf}
\caption{\small The fraction of events that satisfy the requirements
  of one or more categories, for signal and background events.
}
\label{fig:categorisationHisto}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

bin 0: resolved only
bin 1: intermediate only
bin 2: boosted only
bin 3: resolved-intermediate overlap
bin 4: resolved-boosted overlap
bin 5: intermediate-boosted overlap (should be empty due to orthogonal jet multiplicity cuts)

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.65\textwidth]{plots/overlap_categories_C1.pdf}
\caption{\small The fraction of events that satisfy the requirements
  of one or more categories, for signal and background events.
  %
  By construction, there is no overlap between the boosted
  and intermediate categories due to the
   orthogonal jet multiplicity cuts.
}
\label{fig:categorisationHisto}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

bin 0: resolved only
bin 1: intermediate only
bin 2: boosted only
bin 3: resolved-intermediate overlap
bin 4: resolved-boosted overlap

Note that
bin 5: intermediate-boosted overlap (should be empty due to orthogonal jet multiplicity cuts)

### 2015-07-09 paper/sec-intro.tex
work on paper

In this work we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $4b$ final state.
%
Our analysis is based on exploiting the differences between a large
number of kinematic variables in signal and background events.
%
Despite these large QCD multijet backgrounds, by combining the contribution of different final state
topologies, resolved, boosted and intermediate, with a careful optimization
of the analysis strategy, we find that it is possible to obtain a reasonable
good signal discrimination.
%
To further enhance the significance of the measurements, signal and background events
are processed using a Multivariate Analysis (in particular a feed-forward neural
network), that further enhance $S/\sqrt{B}$ up to a value of slightly above 3.0
%
Therefore, we are able to rescue the potential of this final state in a realistic
analysis setup.

>>>>

In this work we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $4b$ final state.
%
Our analysis is based on exploiting the differences between a large
number of kinematic variables in signal and background events.
%
Despite these large QCD multijet backgrounds, by combining the contribution of different final state
topologies, resolved, boosted and intermediate, with a careful optimization
of the analysis strategy, we find that it is possible to obtain a reasonable
good signal discrimination.
%
To further enhance the significance of the measurements, signal and background events
are processed using a Multivariate Analysis (in particular a feed-forward neural
network), that further enhance $S/\sqrt{B}$ up to a value of slightly above 3.0.
%
Therefore, we are able to rescue the potential of this final state in a realistic
analysis setup.
